
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 10: Predictive Modeling - Part 1"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment10.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Use the `Adult Census Income` dataset.  We will predict the income (whether or not it is more than 50k or not) of an adult. Import the dataset.  Partition the data into 80% training and 20% testing. 
```{r}
library(tidyverse)
df <- read_csv("C:\\Users\\student\\OneDrive - Bryant University\\Desktop\\R\\Col7by11.github.io\\adult_census.csv")
df <- df %>% rename(target=income)
df <- df %>% select(-fnlwgt, -capital.gain, -capital.loss, -occupation, -workclass, -native.country, -hours.per.week)
df <- df %>% mutate(target = as.factor(target))

library(caret)
set.seed(2020)
splitIndex <- createDataPartition(df$target, p = .80, list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
```

2. Practice Decision Tree.  Do the follows:

  - Use `rpart` package, create a decision tree with maximum depth of 3. 
  
  - Calculate the accuracy of the model on the testing data. Notice that the positive outcome here is not `1` but `>50K` or `<50K`. 
  
  - Plot the tree
  
  - Plot the variable importance by the tree
```{r}
library(rpart)
tree_model <- rpart(target ~ ., data = df_train,
          control = rpart.control(maxdepth = 3))
library(rattle)
fancyRpartPlot(tree_model)
pred <- predict(tree_model, df_test, type = "class")
cm <- confusionMatrix(data = pred, reference = df_test$target)
cm$overall[1]
tree_model$variable.importance
barplot(tree_model$variable.importance)
```
  
3. Create 3 more trees and compare the testing accuracy of these trees, which tree give the highest testing accuracy.
```{r}
tree_model1 <- rpart(target ~ ., data = df_train,
          control = rpart.control(maxdepth = 4))
fancyRpartPlot(tree_model1)
pred1 <- predict(tree_model1, df_test, type = "class")
cm1 <- confusionMatrix(data = pred1, reference = df_test$target)
cm1$overall[1]
tree_model2 <- rpart(target ~ ., data = df_train,
          control = rpart.control(maxdepth = 5))
fancyRpartPlot(tree_model2)
pred2 <- predict(tree_model2, df_test, type = "class")
cm2 <- confusionMatrix(data = pred2, reference = df_test$target)
cm2$overall[1]
tree_model3 <- rpart(target ~ ., data = df_train,
          control = rpart.control(maxdepth = 2))
fancyRpartPlot(tree_model3)
pred3 <- predict(tree_model3, df_test, type = "class")
cm3 <- confusionMatrix(data = pred3, reference = df_test$target)
cm3$overall[1]
##Tree 2 is giving the highest testing accuracy with max depth of 5
```

4. Practice Random Forest.  Do the follows: 

  - Use `randomForest` package, create a random forest of 1000 trees. 
  
  - Calculate the accuracy of the model on the testing data. 
  
  - Plot the variable importance by the forest
```{r}
library(randomForest)
forest_model = randomForest(target ~ ., data=df_train, ntree = 1000)
pred4 <- predict(forest_model, df_test, type = "class")
cm4 <- confusionMatrix(data = pred, reference = df_test$target, positive = ">50K")
cm4$overall[1]
importance(forest_model)
barplot(forest_model$importance)
```

5. Create 3 more forests and compare the testing accuracy of these forests, which forest give the highest testing accuracy.
```{r}
forest_model1 = randomForest(target ~ ., data=df_train, ntree = 100)
pred4 <- predict(forest_model1, df_test, type = "class")
cm4 <- confusionMatrix(data = pred4, reference = df_test$target, positive = ">50K")
cm4$overall[1]
forest_model2 = randomForest(target ~ ., data=df_train, ntree = 500)
pred5 <- predict(forest_model2, df_test, type = "class")
cm5 <- confusionMatrix(data = pred5, reference = df_test$target, positive = ">50K")
cm5$overall[1]
forest_model3 = randomForest(target ~ ., data=df_train, ntree = 10000)
pred6 <- predict(forest_model3, df_test, type = "class")
cm6 <- confusionMatrix(data = pred6, reference = df_test$target, positive = ">50K")
cm6$overall[1]
##Forest 2 has the hihest testing accuracy with ntree of 10,000
```

6. What is the best model (in term of testing accuracy) among all models (including trees and forests) you have trained?
```{r}
##The second tree is the best model for test accuracy with a value of 0.833 
```

