---
title: "Assignment 3 Extra Credit"
author: "Colby Phillips"
date: "2022-09-28"
output: html_document



---
16.  Find your own dataset, import it and implement the following functions on the data

- head
- str
- names
- mean, min, max
- table
- is.na
- colSums
- class
- cor
- by
- ifelse
- case_when
```{r}
library(lubridate)
library(dplyr)
df <- read.csv("C:\\Users\\student\\OneDrive - Bryant University\\Desktop\\R\\Col7by11.github.io\\adult_census.csv")
head(df)
str(df)
names(df)
mean(df$age, na.rm=TRUE)
min(df$age, na.rm=TRUE)
max(df$age, na.rm=TRUE)
table(df$age)
sum(is.na(df))
colSums(is.na(df))
class(df$age)
cor(df$age, df$education.num)
by(df$age, df$education.num, FUN = mean)
df$sex2 <- ifelse(df$sex=="male",'Male','Female')
df$age2 <- case_when(df$age<18 ~ 'Child',df$age<64 ~ 'Adult',TRUE~'Elder')
```


17.  In the dataset in #16, practice the follows.  You can reuse the code of 16. 

- Create a categorical variable from a continuous variable
- From one categorical variable, create a new categorical variable with fewer categories
```{r}
df$age2 <- case_when(df$age<18 ~ 'Child',df$age<64 ~ 'Adult',TRUE~'Elder')
df$native.country2 <- case_when(df$native.country %in% c('United-States') ~ 'United States', TRUE ~ 'Other')
```


