---
title: "Athlete Top 100 Earnings"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code: embed
    social: menu

runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(flexdashboard)
library(tidyverse)
library(plotly)
library(knitr)
library(DT)
library(lubridate)
df <- read_csv("Forbes Richest Atheletes (Forbes Richest Athletes 1990-2020).csv")

# Create a ggplot object
df <- df %>%  mutate(earnings =`earnings ($ million)`)
df$date <- mdy(df$date)
earnings <- unique(df$earinngs)
unique_sport <- unique(df$Sport)
```

{.sidebar}
=======================================================================

### 1. Athlete Earnings

Athletes have some of the highest wages worldwide.  These earnings can vary across sports and countries. This data set shows the top 100 athlete earnings worldwide.

### 2. Five Input Methods

```{r}
checkboxGroupInput(inputId = "sport_input", 
                   label = h3("Sport"),
                   choices = unique_sport, 
                   inline = TRUE,
                   selected = 'NBA')

radioButtons(inputId = "unique_sport", 
             label = h2("Sport"),
             choices = c('NBA', 'NFL', 'NHL', 'Soccer', 'Tennis', 'Golf', 'Boxing', 'Racing'),
             inline = TRUE,
             selected = 1)

sliderInput(inputId = "earnings_input",
            label = h2("Earnings"),
            min = min(df$earnings, na.rm=TRUE),
            max = max(df$earnings, na.rm=TRUE),
            value=c(0,150))

dateRangeInput(inputId = "date_input", 
               label = h2("Date range"), 
               start = min(df$date), 
               end = max(df$date),
               min = min(df$date), 
               max = max(df$date))

selectInput(inputId = "sport_input", 
            label = h3("Select Sport"),
            choices = unique_sport, 
            selected = 'NBA')
```

Main Tab 1
=======================================================================

Column {data-width=500, .tabset}
-----------------------------------------------------------------------

### Column Tab 1

```{r}
df
```


### Column Tab 2

```{r}
kable(df)
```


### Column Tab 3

```{r}
datatable(df, options = list(
  pageLength = 25
))
```


Main Tab 2
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------


#### Earnings Per Sport

```{r}
library(plotly)
renderPlotly({
  p1 <- df %>% 
    filter(Sport %in% input$sport_input) %>% 
    ggplot(aes(x=earnings))+
    geom_density()
  ggplotly(p1)
})
```

-----------------------------------------------------------------------

Main Tab 3
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------


#### Earnings By Sport

```{r}
renderPlotly({
  p2 <- df %>% 
    filter(Sport==input$unique_sport) %>% 
    ggplot(aes(x=earnings))+
    geom_density()
  ggplotly(p2)
})
```

-----------------------------------------------------------------------

Main Tab 4
=======================================================================

Column {data-width=500, .tabset}
-----------------------------------------------------------------------


### Earnings by Sport

```{r}
renderPlotly({
  p3 <- df %>% 
    filter(earnings>input$earnings_input[1], earnings<input$earnings_input[2]) %>% 
    ggplot(aes(x=Sport))+
    geom_bar()
  ggplotly(p3)
})
```

### What is Bar Chart?

- There are two types of bar charts: geom_bar() and geom_col(). geom_bar() makes the height of the bar proportional to the number of cases in each group (or if the weight aesthetic is supplied, the sum of the weights). 

- If you want the heights of the bars to represent values in the data, use geom_col() instead. geom_bar() uses stat_count() by default: it counts the number of cases at each x position. geom_col() uses stat_identity(): it leaves the data as is.

```{r}
image_url <- "https://s3-us-west-2.amazonaws.com/scorestream-team-profile-pictures/274145/20181010232546_702_mascot300.png"
```

<center><img src="`r image_url`"></center>



Main Tab 5
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------


#### Earnings by Date

```{r}
renderPlotly({
  p4 <- df %>% 
    filter(date > input$date_input[1], date < input$date_input[2]) %>% 
    ggplot(aes(x=earnings))+
    geom_density()
  ggplotly(p4)
})
```

-----------------------------------------------------------------------

Main Tab 6
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------


#### Earnings by Sport

```{r}
renderPlotly({
  p5 <- df %>% 
    filter(Sport==input$sport_input) %>% 
    ggplot(aes(x=earnings))+
    geom_density()
  ggplotly(p5)
})
```